timesliced_random_cell_selection

### 2018-12-06 src/timesliced_random_cell_selection.Rmd
changed no of random points to be selected

```{r}
bckrnd_folder <- "../output/bio/background/raw/"      # path to folder that holds multiple .csv files
bckrnd_list <- list.files(path = bckrnd_folder, pattern="*.csv") # create list of all .csv files in folder
randbckoutput <- "../output/bio/background/rand/" #where the files are to be saved to
# read in each .csv file in file_list and create a data frame with the same name as the .csv file
for (i in 1:length(bckrnd_list)){
  sel <- read.csv(paste(bckrnd_folder, bckrnd_list[i], sep=''))
  sel <- sample_n(sel, 10000) #where 10000 = number of rows to sample (large sample as per maxent)
  write.csv(sel, file = paste0(randbckoutput, bckrnd_list[i]), row.names = FALSE) #dont need to add .csv as it's already in the filename
}
head(sel)  
```

@@

check number of observations 
```{r}
back_rowcount <- nrow(background_all)
back_rowcount
```

@@

```{r}
names(depthbin)[names(depthbin)=="layer_no"] <- "depthlayerno"
names(depthbin)[names(depthbin)=="layer_name"] <- "depth_layer" #this one is just so i don't have to change the column name in the background_all file later
head(depthbin)
```
```{r}
background_all <- merge(background_all, y = depthbin[ , c("depthlayerno", "depth_layer")], by = "depthlayerno", all.x = TRUE)
head(background_all)
```

@@

```{r}
background_all$bottom_depth <- get.depth(bat, background_all[ ,8:9], locator = FALSE)
background_all$bottom_depth <- background_all$bottom_depth[, 3] #this step is because get.bath actually produces it's own dataframe with long, lat, and depth. This is extracting the depth column and deplacing data_aea$bottom_depth with the correct data.
write.csv(background_all,"../output/bio/background_all_lonlat_nafo2_sciname_amo_nao_depthname_bath.csv", row.names = FALSE)
head(background_all)
```

@@

>>>>

```{r}
bckrnd_folder <- "../output/bio/background/raw/"      # path to folder that holds multiple .csv files
bckrnd_list <- list.files(path = bckrnd_folder, pattern="*.csv") # create list of all .csv files in folder
randbckoutput <- "../output/bio/background/rand/" #where the files are to be saved to
# read in each .csv file in file_list and create a data frame with the same name as the .csv file
for (i in 1:length(bckrnd_list)){
  sel <- read.csv(paste(bckrnd_folder, bckrnd_list[i], sep=''))
  sel <- sample_n(sel, 20000) #where 20000 = number of rows to sample (more than 10k as some points will have NA values due to depth - I will select 10000 of these without NA values to create a large sample as per maxent)
  write.csv(sel, file = paste0(randbckoutput, bckrnd_list[i]), row.names = FALSE) #dont need to add .csv as it's already in the filename
}
head(sel)
```

@@

check number of background points in total 
```{r}
back_rowcount <- nrow(background_all)
back_rowcount
```

@@

```{r}
names(depthbin)[names(depthbin)=="layer_no"] <- "depthlayerno"
names(depthbin)[names(depthbin)=="layer_name"] <- "depth_layer" #this one is just so i don't have to change the column name in the background_all file later
head(depthbin)
```

```{r}
background_all <- merge(background_all, y = depthbin[ , c("depthlayerno", "depth_layer")], by = "depthlayerno", all.x = TRUE)
head(background_all)
```

@@

```{r}
background_all$bottom_depth <- get.depth(bat, background_all[ ,8:9], locator = FALSE)
background_all$bottom_depth <- background_all$bottom_depth[, 3] #this step is because get.bath actually produces it's own dataframe with long, lat, and depth. This is extracting the depth column and deplacing data_aea$bottom_depth with the correct data.
write.csv(background_all,"../output/bio/background_all_lonlat_nafo2_sciname_amo_nao_depthname_bath.csv", row.names = FALSE)
head(background_all$bottom_depth)
```

@@

```{r}
comback <- read.csv("../output/bio/background_complete_obs_cels.csv", header = TRUE)
backtempna <- subset(comback, is.na(comback$temp_depth))
backtempna
backtempnasplit <- split(backtempna, list(backtempna$year, backtempna$month), drop = TRUE)
```
